On Determinism of Game Engines used for Simulation-based Autonomous Vehicle Verification

### 2021-04-16 document/ieee_trans/det_ieeetrans.tex
rename top level files, fixed oreilly ref error

\begin{IEEEbiography}{Severin Lemaignan}
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{../other/mugs/tony}}]{Tony Pipe}
Tony Pipe received his BSc (Hons.) degree in Electronic Engineering from Warwick in 1979 and, after an eight-year period in industry that included running a small company, received his PhD in Robotics from the University of the West of England (UWE) in 1997. Since 2010 he has been a Professor of Robotics and Autonomous Systems at UWE. He was a founding member of the Bristol Robotics Laboratory (BRL), and acted as one of its two Deputy Directors from its inception in 2006 until 2020. His research interests focus on safe and correct operation whilst in close-proximity to human beings. He has co-authored over 200 international refereed publications, supervised 35 PhDs, and created a BRL income of >£10M since 2013. He has acted as BRL-UWE PI on the EPSRC grant ‘Trustworthy Robotic Assistants’, the Programme/Hub grants ‘Robotics for Nuclear Environments’ and ‘National Centre for Nuclear Robotics’, and the Centre for Doctoral Training in Robotics and Autonomous Systems. Prof. Pipe has been involved with Connected Autonomous Vehicle research and development since 2015 via the Innovate UK/CCAV funded projects VENTURER, FLOURISH, MultiCAV, CAPRI, ROBOPILOT and CAV-Forth.
\end{IEEEbiography}

>>>>

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{../other/mugs/severin}}]{S\'everin Lemaignan}
S\'everin Lemaignan is Associate Professor in Social Robotics and AI at the Bristol Robotics Laboratory, University of the West of England, Bristol. He obtained a joint PhD in Cognitive Robotics from the CNRS/LAAS (France) and the Technical University of Munich (Germany) in 2012. He then joined the EPFL (Switzerland) and Plymouth University (UK) as post-doc, then lecturer in Robotics until 2018, when he joined the Bristol Robotics Lab. His research interest primarily concerns the socio-cognitive aspects of human-robot interaction and he has been focusing his recent experimental work on child-robot interaction and human-in-the-loop machine learning for social robots. Pr. S\'everin Lemaignan has been involved in several European projects related to social and cognitive robotics (CHRIS, DREAM, L2TOR) and was  awarded in 2015 a EU H2020 Marie Sk\l{}odowska-Curie Individual Fellowship for his project on robots and theory of mind.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{../other/mugs/tony}}]{Tony Pipe}
Tony Pipe received his BSc (Hons.) degree in Electronic Engineering from Warwick in 1979 and, after an eight-year period in industry that included running a small company, received his PhD in Robotics from the University of the West of England (UWE) in 1997. Since 2010 he has been a Professor of Robotics and Autonomous Systems at UWE. He was a founding member of the Bristol Robotics Laboratory (BRL), and acted as one of its two Deputy Directors from its inception in 2006 until 2020. His research interests focus on safe and correct operation whilst in close-proximity to human beings. He has co-authored over 200 international refereed publications, supervised 35 PhDs, and created a BRL income of \pounds£10M since 2013. He has acted as BRL-UWE PI on the EPSRC grant ‘Trustworthy Robotic Assistants’, the Programme/Hub grants ‘Robotics for Nuclear Environments’ and ‘National Centre for Nuclear Robotics’, and the Centre for Doctoral Training in Robotics and Autonomous Systems. Prof. Pipe has been involved with Connected Autonomous Vehicle research and development since 2015 via the Innovate UK/CCAV funded projects VENTURER, FLOURISH, MultiCAV, CAPRI, ROBOPILOT and CAV-Forth.
\end{IEEEbiography}
